---
title: "Figures"
author: "Marcus Beck"
output: 
  html_document:
  toc: yes
self_contained: yes
---

```{r, echo = F}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE)
```


1.	The new index works. [Demonstrate basic performance parameters, like lack of bias within reference sites, and good responsiveness to a few stressor gradients]
2.	The new index makes our region (or watersheds/land use classes) look good/bad [calculate extent of stream-miles in good/bad classes, based on reference percentiles; compare to results from earlier algae IBIs]
3.	The new index is complementary to the CSCI [demonstrate agreement, and/or insightful disagreements]

```{r}
# libraries
library(tidyverse)
library(rgdal)
library(rgeos)
library(sp)
library(raster)

# data
data(indat)
data(evdat)
data(sheds)
```

```{r, fig.height = 5, fig.width = 9}
tycol <- RColorBrewer::brewer.pal(3, 'RdYlGn') %>% 
  rev
ggplot(indat, aes(x = type, y = scr)) + 
  geom_boxplot(outlier.size = 1, aes(fill = type)) + 
  facet_grid(ind ~ tax) +
  scale_fill_manual(values = tycol) +
  scale_y_continuous('Index Score') + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    axis.title.x = element_blank(), 
    panel.border = element_rect(colour = 'black', fill = NA, size = 0.5), 
    legend.position = 'none'
  ) 
```

