---
title: "Figures"
author: "Marcus Beck"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
self_contained: yes
---

```{r, echo = F}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, fig.path = 'figs/')
```

### Overview

*From Rafi:* The big message is that these new indices enhance our ability to manage streams and implement policies like biological objectives/biointegrity-biostimulatory policies. This index is going to help both the regulators and regulated community alike by giving them a new way to assess biological condition.

Graphics should demonstrate:

1.	The new index works. [Demonstrate basic performance parameters, like lack of bias within reference sites, and good responsiveness to a few stressor gradients]

2.	The new index makes our region (or watersheds/land use classes) look good/bad [calculate extent of stream-miles in good/bad classes, based on reference percentiles; compare to results from earlier algae IBIs]

3.	The new index is complementary to the CSCI [demonstrate agreement, and/or insightful disagreements]

```{r setup}
# libraries
library(tidyverse)
library(broom)
library(rgdal)
library(rgeos)
library(sp)
library(raster)
library(gridExtra)
library(micromap)
library(plotly)
source('R/funcs.R')

# data
data(indat)
data(evdat)
data(sheds)
data(aldat)

# color palettes
ctcol <- RColorBrewer::brewer.pal(3, 'RdYlGn') %>% 
  rev
tycol <- RColorBrewer::brewer.pal(9, 'PRGn') %>% 
  rev
ptcol <- RColorBrewer::brewer.pal(9, 'Set1')[c(1:3)]
```

### Score distributions

```{r box, fig.height = 5, fig.width = 9}
ggplot(indat, aes(x = type, y = scr)) + 
  geom_boxplot(outlier.size = 1, aes(fill = type), alpha = 0.7) + 
  facet_grid(ind ~ tax) +
  scale_fill_manual(values = ctcol) +
  scale_y_continuous('Index Score') + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    axis.title.x = element_blank(), 
    panel.border = element_rect(colour = 'black', fill = NA, size = 0.5), 
    legend.position = 'none'
  ) 
```

```{r scrchcls, fig.height = 5, fig.width = 9}
toplo <- indat %>% 
  dplyr::select(chcls, scr, ind, tax) %>% 
  na.omit

ggplot(toplo, aes(x = chcls, y = scr, fill = chcls)) +
  geom_boxplot(alpha = 0.7) +
  facet_grid(ind ~ tax) + 
  scale_y_continuous('Index Score') +
  scale_fill_manual(values = ptcol[c(3, 1, 2)]) + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    axis.title.x = element_blank(), 
    panel.border = element_rect(colour = 'black', fill = NA, size = 0.5), 
    legend.position = 'none'
  ) 
```

```{r bar, fig.height = 8, fig.width = 8}
# colors
colfun <- rev(tycol) %>% 
  colorRampPalette

# format for plots
toplo <- indat %>% 
  group_by(ind, tax, SMC_Name) %>% 
  summarise(
    mnval = mean(scr), 
    loval = confint(lm(scr ~ 1))[1],
    hival = confint(lm(scr ~ 1))[2]
  ) %>% 
  ungroup %>% 
  mutate(
    cols = colfun(length(mnval))[rank(mnval)]
  ) %>% 
  split(., .[, c('ind', 'tax')])

# arrange each barplot separately
for(i in seq_along(names(toplo))){
  
  tmp <- toplo[[i]] %>% 
    arrange(mnval) %>% 
    mutate(SMC_Name = factor(SMC_Name, levels = SMC_Name))
  
  p <- ggplot(tmp, aes(x = SMC_Name, y = mnval)) + 
    geom_bar(stat = 'identity', fill = tmp$cols, col = 'grey') +
    geom_errorbar(aes(ymin = loval, ymax = hival), width = 0.2) +
    facet_wrap(ind ~ tax) +
    scale_y_continuous('Index Score', expand = c(0, 0), limits = c(0, 1.1)) + 
    coord_flip() + 
    theme_minimal() +
    theme(
      axis.text.y = element_text(size = 7), 
      axis.title.y = element_blank(), 
      axis.title.x = element_blank(),
      panel.border = element_rect(colour = 'black', fill = NA, size = 0.5),
      legend.position = 'none', 
      panel.grid.minor = element_blank(), 
      panel.grid.major = element_blank()
    ) 
  p <- ggplot_gtable(ggplot_build(p))
  
  assign(paste0('p', i), p) 
  
}

# Get the widths
maxWidth = grid::unit.pmax(p1$widths[2:3], p2$widths[2:3], p3$widths[2:3], p4$widths[2:3], p5$widths[2:3], p6$widths[2:3])

# Set the widths
p1$widths[2:3] <- maxWidth
p2$widths[2:3] <- maxWidth
p3$widths[2:3] <- maxWidth
p4$widths[2:3] <- maxWidth
p5$widths[2:3] <- maxWidth
p6$widths[2:3] <- maxWidth

grid.arrange(p1, p2, p3, p4, p5, p6, ncol = 2, bottom = 'Index Score')

```

```{r chloro, fig.height = 8, fig.width = 9}
# add shc shed names to fortified shapefile
key <- sheds@data %>% 
  rownames_to_column('id') %>% 
  dplyr::select(id, SMC_Name)
shd <- tidy(sheds) %>% 
  left_join(key, by = 'id')

# get percent sites in each category by type
# merge with fortified sheds
toplo <- indat %>% 
  group_by(SMC_Name, ind, tax, scrcat) %>% 
  summarise(
    n = length(scrcat)
  ) %>% 
  group_by(SMC_Name, ind, tax) %>% 
  nest %>% 
  mutate(
    ntot = map(data, ~ sum(.x$n) %>% rep(2))
    ) %>% 
  unnest %>% 
  ungroup %>% 
  mutate(n = 100 * n / ntot) %>% 
  filter(scrcat %in% 'Hi') %>%
  left_join(shd, ., by = 'SMC_Name') %>% 
  rename(`% sites above\nthreshold` = n)

ggplot() + 
  geom_polygon(data = toplo, 
               aes(x = long, y = lat, fill = `% sites above\nthreshold`, group = group), 
               colour = 'gray', alpha = 0.8
               ) + 
  facet_wrap(tax ~ ind, ncol = 2) + 
  coord_map() + 
  scale_fill_gradientn(colors = rev(tycol)) + 
  theme_minimal() +
  theme(
    axis.title.y = element_blank(), 
    axis.title.x = element_blank(),
    panel.border = element_rect(colour = 'black', fill = NA, size = 0.5)
  )
```

### Hi/lo distributions

```{r mapall, fig.height = 8, fig.width = 9}
# add shc shed names to fortified shapefile
key <- sheds@data %>% 
  rownames_to_column('id') %>% 
  dplyr::select(id, SMC_Name)
shd <- tidy(sheds) %>% 
  left_join(key, by = 'id')

# all index data
toplo <- indat %>% 
  rename(`Index\ncategory` = scrcat)

ggplot(toplo) + 
  geom_polygon(data = shd, 
               aes(x = long, y = lat, group = group), 
               colour = 'gray', fill = 'lightgrey', alpha = 0.8
               ) + 
  geom_point(aes(x = lon, y = lat, colour = `Index\ncategory`), alpha = 0.7) +
  facet_wrap(tax ~ ind, ncol = 2) + 
  coord_map() + 
  scale_colour_manual(values = ctcol[c(1, 3)]) + 
  theme_minimal() +
  theme(
    axis.title.y = element_blank(), 
    axis.title.x = element_blank(),
    panel.border = element_rect(colour = 'black', fill = NA, size = 0.5)
  )
```

```{r cattyp, fig.height = 5, fig.width = 9}
# get percent sites in each category by type
toplo <- indat %>% 
  group_by(type, ind, tax, scrcat) %>% 
  summarise(
    n = length(scrcat)
  ) %>% 
  ungroup %>% 
  rename(`Index\ncategory` = scrcat)
  
ggplot(toplo, aes(x = type, y = n, fill = `Index\ncategory`)) +
  geom_bar(stat = 'identity', position = 'fill', colour = 'grey', alpha = 0.8, width = 0.75) + 
  facet_grid(ind ~ tax) + 
  scale_y_continuous('Proportion', expand = c(0, 0)) +
  scale_fill_manual(values = ctcol[c(1, 3)]) + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    axis.title.x = element_blank(), 
    panel.border = element_rect(colour = 'black', fill = NA, size = 0.5), 
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
  ) 
```

```{r catchcls, fig.height = 5, fig.width = 9}
# get percent sites in each category by type
toplo <- indat %>% 
  group_by(chcls, ind, tax, scrcat) %>% 
  summarise(
    n = length(scrcat)
  ) %>% 
  ungroup %>% 
  rename(`Index\ncategory` = scrcat) %>% 
  na.omit
  
ggplot(toplo, aes(x = chcls, y = n, fill = `Index\ncategory`)) +
  geom_bar(stat = 'identity', position = 'fill', colour = 'grey', alpha = 0.8, width = 0.75) + 
  facet_grid(ind ~ tax) + 
  scale_y_continuous('Proportion', expand = c(0, 0)) +
  scale_fill_manual(values = ctcol[c(1, 3)]) + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    axis.title.x = element_blank(), 
    panel.border = element_rect(colour = 'black', fill = NA, size = 0.5), 
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
  ) 
```

```{r catshed, fig.height = 8, fig.width = 8}

# get percent sites in each category by type
toplo <- indat %>% 
  group_by(SMC_Name, ind, tax, scrcat) %>% 
  summarise(
    n = length(scrcat)
  ) %>% 
  group_by(SMC_Name, ind, tax) %>% 
  nest %>% 
  mutate(
    ntot = map(data, ~ sum(.x$n) %>% rep(2))
    ) %>% 
  unnest %>% 
  ungroup %>% 
  mutate(n = n / ntot) %>% 
  rename(`Index\ncategory` = scrcat) %>% 
  split(., .[, c('ind', 'tax')])

# arrange each barplot separately
for(i in seq_along(names(toplo))){
  
  tmp <- toplo[[i]] %>% 
    spread(`Index\ncategory`, n) %>% 
    arrange(Hi) %>% 
    mutate(SMC_Name = factor(SMC_Name, levels = SMC_Name)) %>% 
    gather(`Index category`, 'n', Hi:Lo)
  
  p <- ggplot(tmp, aes(x = SMC_Name, y = n, fill = `Index category`)) + 
    geom_bar(stat = 'identity',  position = position_stack(reverse = TRUE), colour = 'grey', alpha = 0.8, width = 0.75) +
    facet_wrap(ind ~ tax) +
    scale_fill_manual(values = ctcol[c(1, 3)]) + 
    scale_y_continuous('Proportion', expand = c(0, 0)) + 
    coord_flip() + 
    theme_minimal() +
    theme(
      axis.text.y = element_text(size = 7), 
      axis.title.y = element_blank(), 
      axis.title.x = element_blank(),
      panel.border = element_rect(colour = 'black', fill = NA, size = 0.5),
      legend.position = 'top', 
      panel.grid.minor = element_blank(), 
      panel.grid.major = element_blank()
    )
  
  # get legend if last
  if(i == length(toplo))
    pleg <- g_legend(p)
  
  p <- p + theme(legend.position = 'none')
  p <- ggplot_gtable(ggplot_build(p))
  
  assign(paste0('p', i), p) 
  
}

# Get the widths
maxWidth = grid::unit.pmax(p1$widths[2:3], p2$widths[2:3], p3$widths[2:3], p4$widths[2:3], p5$widths[2:3], p6$widths[2:3])

# Set the widths
p1$widths[2:3] <- maxWidth
p2$widths[2:3] <- maxWidth
p3$widths[2:3] <- maxWidth
p4$widths[2:3] <- maxWidth
p5$widths[2:3] <- maxWidth
p6$widths[2:3] <- maxWidth

grid.arrange(
  pleg, 
  arrangeGrob(p1, p2, p3, p4, p5, p6, ncol = 2),
  heights = c(0.1, 1),
  bottom = 'Proportion of stream sites'
  )

```

### Relationships with environmental variables

#### Scatterplots {.tabset .tabset-fade .tabset-pills}

```{r setscat}
evvar <- list(
  varorg = c('Phosphorus_as_P_mgPerL', 'Nitrogen_Total_mgPerL', 'XCDENMID', 'PCT_SAFN', 'SpecificConductivity_uSPercm', 'Temperature_Deg_C'), 
  varnew = c('Phosphorus (mg/L)', 'Total Nitrogen (mg/L)', '% Shading', '% Sands and Fines', 'Conductivity (mS/cm)', 'Temperature (C)')
)

# sites and channel cls
chcls <- indat %>% 
  dplyr::select(id, chcls) %>% 
  unique

# old indices
toplo_old <- evdat[, c('id', evvar$varorg)] %>% 
  left_join(aldat, ., by = 'id') %>% 
  inner_join(chcls, ., by = 'id') %>% 
  rename(
    `Index Score` = scr,
    `Channel Type` = chcls
  ) %>% 
  .[, c('id', 'ind', 'Channel Type', 'Index Score', evvar$varorg)] %>% 
  filter(!`Channel Type` %in% 'All or partially earthen' & !is.na(`Channel Type`)) %>% 
  mutate(
    ind = factor(ind, levels = c('D18', 'S2', 'H20'))
  )

# new indices
toplo_new <- evdat[, c('id', evvar$varorg)] %>% 
  left_join(indat, ., by = 'id') %>% 
  rename(
    `Index Score` = scr,
    `Channel Type` = chcls
  ) %>% 
  .[, c('id', 'ind', 'Channel Type', 'tax', 'thr', 'Index Score', evvar$varorg)] %>% 
  filter(!`Channel Type` %in% 'All or partially earthen' & !is.na(`Channel Type`))

# base theme
pbase <- theme_minimal() +
  theme(
    panel.border = element_rect(colour = 'black', fill = NA, size = 0.5),
    legend.position = 'top', 
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank()
  )
```

##### Phosphorus
```{r byphos, fig.height = 8, fig.width = 8}
pold <- ggplot(toplo_old, aes(x = Phosphorus_as_P_mgPerL, y = `Index Score`, colour = `Channel Type`)) +
  geom_point(alpha = 0.7, size = 1.5) +
  geom_smooth(method = 'lm', se = FALSE) +
  facet_wrap( ~ ind, ncol = 3) +
  scale_colour_manual(values = ptcol) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_log10('Phosphorus (mg/L)') +
  pbase

pnew <- ggplot(toplo_new, aes(x = Phosphorus_as_P_mgPerL, y = `Index Score`, colour = `Channel Type`)) +
  geom_point(alpha = 0.7, size = 1.5) +
  geom_smooth(method = 'lm', se = FALSE) +
  geom_hline(aes(yintercept = thr), linetype = 'dashed') +
  facet_grid(ind ~ tax) +
  scale_colour_manual(values = ptcol) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_log10('Phosphorus (mg/L)') +
  pbase

grid.arrange(pold, pnew, ncol = 1, heights = c(0.6, 1))
```

##### Nitrogen
```{r bynitr, fig.height = 8, fig.width = 8}
pold <- ggplot(toplo_old, aes(x = Nitrogen_Total_mgPerL, y = `Index Score`, colour = `Channel Type`)) +
  geom_point(alpha = 0.7, size = 1.5) +
  geom_smooth(method = 'lm', se = FALSE) +
  facet_wrap( ~ ind, ncol = 3) +
  scale_colour_manual(values = ptcol) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_log10('Total Nitrogen (mg/L)') +
  pbase

pnew <- ggplot(toplo_new, aes(x = Nitrogen_Total_mgPerL, y = `Index Score`, colour = `Channel Type`)) +
  geom_point(alpha = 0.7, size = 1.5) +
  geom_smooth(method = 'lm', se = FALSE) +
  geom_hline(aes(yintercept = thr), linetype = 'dashed') +
  facet_grid(ind ~ tax) +
  scale_colour_manual(values = ptcol) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_log10('Total Nitrogen (mg/L)') +
  pbase

grid.arrange(pold, pnew, ncol = 1, heights = c(0.6, 1))
```

##### % Shading
```{r byshad, fig.height = 8, fig.width = 8}
pold <- ggplot(toplo_old, aes(x = XCDENMID, y = `Index Score`, colour = `Channel Type`)) +
  geom_smooth(method = 'lm', se = FALSE) +
  geom_point(alpha = 0.7, size = 1.5) +
  facet_wrap( ~ ind, ncol = 3) +
  scale_colour_manual(values = ptcol) +
  scale_x_continuous('% Shading') +
  scale_y_continuous(expand = c(0, 0)) +
  pbase

pnew <- ggplot(toplo_new, aes(x = XCDENMID, y = `Index Score`, colour = `Channel Type`)) +
  geom_smooth(method = 'lm', se = FALSE) +
  geom_point(alpha = 0.7, size = 1.5) +
  geom_hline(aes(yintercept = thr), linetype = 'dashed') +
  facet_grid(ind ~ tax) +
  scale_colour_manual(values = ptcol) +
  scale_x_continuous('% Shading') +
  scale_y_continuous(expand = c(0, 0)) +
  pbase

grid.arrange(pold, pnew, ncol = 1, heights = c(0.6, 1))
```

##### % Sands and Fines
```{r bysafn, fig.height = 8, fig.width = 8}
pold <- ggplot(toplo_old, aes(x = PCT_SAFN, y = `Index Score`, colour = `Channel Type`)) +
  geom_point(alpha = 0.7, size = 1.5) +
  geom_smooth(method = 'lm', se = FALSE) +
  facet_wrap( ~ ind, ncol = 3) +
  scale_colour_manual(values = ptcol) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous('% Sands and Fines') +
  pbase

pnew <- ggplot(toplo_new, aes(x = PCT_SAFN, y = `Index Score`, colour = `Channel Type`)) +
  geom_point(alpha = 0.7, size = 1.5) +
  geom_smooth(method = 'lm', se = FALSE) +
  geom_hline(aes(yintercept = thr), linetype = 'dashed') +
  facet_grid(ind ~ tax) +
  scale_colour_manual(values = ptcol) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous('% Sands and Fines') +
  pbase

grid.arrange(pold, pnew, ncol = 1, heights = c(0.6, 1))
```

##### Conductivity
```{r bycondo, fig.height = 8, fig.width = 8}
pold <- ggplot(toplo_old, aes(x = SpecificConductivity_uSPercm, y = `Index Score`, colour = `Channel Type`)) +
  geom_point(alpha = 0.7, size = 1.5) +
  geom_smooth(method = 'lm', se = FALSE) +
  facet_wrap( ~ ind, ncol = 3) +
  scale_colour_manual(values = ptcol) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous('Conductivity (uS/Cm)') +
  pbase

pnew <- ggplot(toplo_new, aes(x = SpecificConductivity_uSPercm, y = `Index Score`, colour = `Channel Type`)) +
  geom_point(alpha = 0.7, size = 1.5) +
  geom_smooth(method = 'lm', se = FALSE) +
  geom_hline(aes(yintercept = thr), linetype = 'dashed') +
  facet_grid(ind ~ tax) +
  scale_colour_manual(values = ptcol) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous('Conductivity (uS/Cm)') +
  pbase

grid.arrange(pold, pnew, ncol = 1, heights = c(0.6, 1))
```

##### Temperature
```{r bytempo, fig.height = 8, fig.width = 8}
pold <- ggplot(toplo_old, aes(x = Temperature_Deg_C, y = `Index Score`, colour = `Channel Type`)) +
  geom_point(alpha = 0.7, size = 1.5) +
  geom_smooth(method = 'lm', se = FALSE) +
  facet_wrap( ~ ind, ncol = 3) +
  scale_colour_manual(values = ptcol) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous('Temperature (C)') +
  pbase

pnew <- ggplot(toplo_new, aes(x = Temperature_Deg_C, y = `Index Score`, colour = `Channel Type`)) +
  geom_point(alpha = 0.7, size = 1.5) +
  geom_smooth(method = 'lm', se = FALSE) +
  geom_hline(aes(yintercept = thr), linetype = 'dashed') +
  facet_grid(ind ~ tax) +
  scale_colour_manual(values = ptcol) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous('Temperature (C)') +
  pbase

grid.arrange(pold, pnew, ncol = 1, heights = c(0.6, 1))
```

#### Micromaps, old {.tabset .tabset-fade .tabset-pills}

```{r microold, results = 'hide', fig.show = 'hide'}
# prep aldat for micromap
# merge with some evdat variable

evvar <- c('Phosphorus_as_P_mgPerL', 'Nitrogen_Total_mgPerL')
invar <- c('D18', 'S2', 'H20')

shds <- indat %>% 
  dplyr::select(id, SMC_Name) %>% 
  unique

for(i in seq_along(invar)){
  
  inv <- invar[i]
  
  # subset and summarize data by inputs
  toplo <- evdat[, c('id', evvar)]
  names(toplo)[names(toplo) %in% evvar] <- c('evvar1', 'evvar2')
  toplo <- toplo %>% 
    left_join(aldat, ., by = 'id') %>% 
    filter(ind %in% inv) %>% 
    inner_join(shds, by = 'id') %>% 
    group_by(SMC_Name) %>% 
    summarise(
      scr = mean(scr, na.rm = TRUE), 
      evvar1 = mean(evvar1, na.rm = TRUE),
      evvar2 = mean(evvar2, na.rm = TRUE)
    ) %>% 
    ungroup %>% 
    as.data.frame
  
  # create map table for polygons
  polys <- create_map_table(sheds, 'SMC_Name')
  
  # micromap globals
  ptsz <- 1.5
  pwds <- 0.8
  xszs <- 0.5
  bgcl <- 'gray95'
  
  # plot
  p <- mmplot(stat.data = toplo,
    map.data = polys,
    panel.types = c('dot_legend', 'labels', 'dot', 'dot', 'dot', 'map'),
    panel.data = list(NA, 'SMC_Name', 'scr', 'evvar1', 'evvar2', NA), 
    grouping = 3,
    ord.by = 'scr',  
    plot.width = 9,
    plot.height = 4,
    median.row = F,
    colors = rev(tycol),
    map.link = c('SMC_Name', 'ID'),
    panel.att = list(
        list(2, 
             header = 'SMC watershed', 
             text.size = 0.6, 
             align = 'left', 
             panel.width = 1
             ),
        list(3, 
             header = inv, 
             point.size = ptsz, 
             panel.width = pwds, 
             xaxis.labels.size = xszs, 
             graph.bgcolor = bgcl
             ),
        list(4, 
             header = 'Phosphorus\n(mg/L)', 
             point.size = ptsz, 
             panel.width = pwds, 
             xaxis.labels.size = xszs, 
             graph.bgcolor = bgcl
             ), 
        list(5, 
             header = 'Total Nitrogen\n(mg/L', 
             point.size = ptsz, 
             panel.width = pwds, 
             xaxis.labels.size = xszs, 
             graph.bgcolor = bgcl
             )
      ),
    plot.panel.spacing = 0
    )
  
  assign(paste0('p', i), p)
  
  }

```

##### D18
```{r microd18, fig.height = 5, fig.width = 7.5}
p1
```

##### S2
```{r micros2, fig.height = 5, fig.width = 7.5}
p2
```

##### H20
```{r microh20, fig.height = 5, fig.width = 7.5}
p3
```

#### Micromaps, new {.tabset .tabset-fade .tabset-pills}

```{r micronew, results = 'hide', fig.show = 'hide'}
# prep indat for micromap
# merge with some evdat variable

evvar <- c('Phosphorus_as_P_mgPerL', 'Nitrogen_Total_mgPerL')
intx <- crossing(
  invar = c('O/E', 'pMMI'), 
  txvar = c('Diatom', 'Soft-bodied', 'Hybrid')
  )

for(i in 1:nrow(intx)){
  
  invar <- intx[i, ]$invar
  txvar <- intx[i, ]$txvar
  
  # subset and summarize data by inputs
  toplo <- evdat[, c('id', evvar)]
  names(toplo)[names(toplo) %in% evvar] <- c('evvar1', 'evvar2')
  toplo <- toplo %>% 
    left_join(indat, ., by = 'id') %>% 
    filter(ind %in% invar & tax %in% txvar) %>% 
    group_by(SMC_Name) %>% 
    summarise(
      scr = mean(scr, na.rm = TRUE), 
      evvar1 = mean(evvar1, na.rm = TRUE),
      evvar2 = mean(evvar2, na.rm = TRUE)
    ) %>% 
    ungroup %>% 
    as.data.frame
  
  # create map table for polygons
  polys <- create_map_table(sheds, 'SMC_Name')
  
  # micromap globals
  ptsz <- 1.5
  pwds <- 0.8
  xszs <- 0.5
  bgcl <- 'gray95'
  
  # plot
  p <- mmplot(stat.data = toplo,
    map.data = polys,
    panel.types = c('dot_legend', 'labels', 'dot', 'dot', 'dot', 'map'),
    panel.data = list(NA, 'SMC_Name', 'scr', 'evvar1', 'evvar2', NA), 
    grouping = 3,
    ord.by = 'scr',  
    plot.width = 9,
    plot.height = 4,
    median.row = F,
    colors = rev(tycol),
    map.link = c('SMC_Name', 'ID'),
    panel.att = list(
        list(2, 
             header = 'SMC watershed', 
             text.size = 0.6, 
             align = 'left', 
             panel.width = 1
             ),
        list(3, 
             header = paste(invar, txvar, sep = ', '), 
             point.size = ptsz, 
             panel.width = pwds, 
             xaxis.labels.size = xszs, 
             graph.bgcolor = bgcl
             ),
        list(4, 
             header = 'Phosphorus\n(mg/L)', 
             point.size = ptsz, 
             panel.width = pwds, 
             xaxis.labels.size = xszs, 
             graph.bgcolor = bgcl
             ), 
        list(5, 
             header = 'Total Nitrogen\n(mg/L', 
             point.size = ptsz, 
             panel.width = pwds, 
             xaxis.labels.size = xszs, 
             graph.bgcolor = bgcl
             )
      ),
    plot.panel.spacing = 0
    )
  
  assign(paste0('p', i), p)
  
  }

```

##### O/E, diatoms
```{r microoedia, fig.height = 5, fig.width = 7.5}
p1
```


##### O/E, hybrid
```{r microoehyb, fig.height = 5, fig.width = 7.5}
p2
```


##### O/E, soft-bodied
```{r microoesft, fig.height = 5, fig.width = 7.5}
p3
```


##### pMMI, diatoms
```{r micrommdia, fig.height = 5, fig.width = 7.5}
p4
```


##### pMMI, hybrid
```{r micrommhyb, fig.height = 5, fig.width = 7.5}
p5
```


##### pMMI, soft-bodied
```{r micrommsft, fig.height = 5, fig.width = 7.5}
p6
```


### Comparison with existing algal indices {.tabset .tabset-fade .tabset-pills}

#### S2
```{r cmps2, fig.height = 5, fig.width = 7}

alind <- c('S2', 'H20', 'D18')
taxs <- c('Soft-bodied', 'Hybrid', 'Diatom')
lms <- c(0, 1.6)

for(i in seq_along(alind)){
  
  togrb <- alind[i]
  txgrb <- taxs[i]
  xlab <- paste(togrb, 'Index Score')

  toplo <- aldat[aldat$ind %in% togrb, ] %>% 
    rename(cmp = scr) %>% 
    dplyr::select(-ind) %>% 
    left_join(indat, ., by = 'id') %>% 
    filter(tax %in% txgrb) %>% 
    mutate(scrdf = scr - cmp)
  
  pA <- ggplot(toplo, aes(x = cmp, y = scr)) + 
    geom_point(alpha = 0.6, size = 1) +
    geom_abline(intercept = 0, slope = 1, linetype = 'dashed') +
    geom_smooth(method = 'lm', se = F) +
    facet_wrap( ~ ind, ncol = 1) +
    scale_colour_manual(values = ptcol) +
    scale_y_continuous('New Index Score', limits = lms) +
    scale_x_continuous(limits = lms) +
    pbase +
    theme(axis.title.x = element_blank())
  
  pB <- ggplot(toplo, aes(x = cmp, y = scrdf)) + 
    geom_point(alpha = 0.6, size = 1) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_smooth(method = 'lm', se = F) +
    facet_wrap( ~ ind, ncol = 1) +
    scale_colour_manual(values = ptcol) +
    scale_y_continuous('New - Old Index Score') +
    scale_x_continuous(limits = lms) +
    pbase +
    theme(axis.title.x = element_blank())
  
  assign(paste0('pA_', togrb), pA)
  assign(paste0('pB_', togrb), pB)
  
}

grid.arrange(pA_S2, pB_S2, ncol = 2, bottom = 'S2 Index Score')
```

#### H20
```{r cmph20, fig.height = 5, fig.width = 7}
grid.arrange(pA_H20, pB_H20, ncol = 2, bottom = 'H20 Index Score')
```

#### D18
```{r cmpd18, fig.height = 5, fig.width = 7}
grid.arrange(pA_D18, pB_D18, ncol = 2, bottom = 'D18 Index Score')
```
